Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-05-04 doc/RMD/mlg-mcg.Rmd
add community detection and indication on graphs

```{r}
make_mcgmlg_graph <- function(x){
  gdf <- mutate(x, MLG = paste0('MLG.', MLG))
  MLGS <- gdf %>% 
    group_by(MLG) %>%
    summarize(size = sum(Freq)) %>%
    rename(vertex = MLG)
  MCGS <- gdf %>% 
    group_by(MCG) %>%
    summarize(size = sum(Freq)) %>%
    rename(vertex = MCG)
  VAT <- bind_rows(MLGS, MCGS)
  g <- gdf %>% 
    select(MCG, MLG, Freq) %>%
    rename(weight = Freq) %>%
    graph_from_data_frame(vertices = VAT)
  V(g)$type <- ifelse(grepl("MLG", V(g)$name), "Multilocus Genotype", "Mycelial Compatibility Group")
  g
}
g <- make_mcgmlg_graph(mcgmlg)
osize <- V(g)$size
```

@@

mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, fill = type)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), color = type, size = size/10), show.legend = FALSE) +
  coord_fixed() +
  scale_edge_width(range = c(0.25, 1.5)) +
  # scale_edge_color_viridis(option = "C", end = 0.9) +
  scale_color_manual(values = c("white", "black")) +
  scale_fill_manual(values = c("black", "white")) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  ggtitle("Relation of Multilocus Genotypes and MCGs")

@@

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% mcgs$MCG[1:5])
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
set.seed(2017-05-03)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "nicely")
t5g <- mcg_mlg_graph %+% top5lay + ggtitle("Top 5 Mycelial Compatibility Groups and associated MLGs")
ggsave(t5g, file = file.path("results", "figures", "publication", "FigureS2B.svg"), width = 88, height = 88, units = "mm")
```

>>>>

```{r}
make_mcgmlg_graph <- function(x){
  gdf <- mutate(x, MLG = paste0('MLG.', MLG))
  MLGS <- gdf %>% 
    group_by(MLG) %>%
    summarize(size = sum(Freq)) %>%
    rename(vertex = MLG)
  MCGS <- gdf %>% 
    group_by(MCG) %>%
    summarize(size = sum(Freq)) %>%
    rename(vertex = MCG)
  VAT <- bind_rows(MLGS, MCGS)
  g <- gdf %>% 
    select(MCG, MLG, Freq) %>%
    rename(weight = Freq) %>%
    graph_from_data_frame(vertices = VAT)
  V(g)$type <- ifelse(grepl("MLG", V(g)$name), "Multilocus Genotype", "Mycelial Compatibility Group")
  g
}

add_communities <- function(g, clusters){
  comm <- communities(clusters)
  commlist <- setNames(rep(names(comm), lengths(comm)), unlist(comm, use.names = FALSE))
  V(g)$community <- commlist[V(g)$name]
  g
}
g <- make_mcgmlg_graph(mcgmlg)
g <- add_communities(g, cluster_walktrap(g))
osize <- V(g)$size
```

@@

the_communities <- data_frame(vertex = lay2$name, community = lay2$community) %>%
  group_by(community) %>%
  mutate(comm = ifelse(n() > 10, paste("Community", community), "Other Communities (n < 10)")) %>%
  mutate(comm = forcats::fct_infreq(comm) %>% forcats::fct_shift(-1L))
lay2$community <- the_communities$comm

mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, lty = type, fill = community)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = ifelse(grepl("ther", community), "A", ifelse(grepl("3", community), "B", "C")), 
                     size = size/10), 
                 show.legend = FALSE) +
  coord_fixed() +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_color_manual(values = c("white", "grey75", "black")) +
  scale_fill_viridis(direction = -1, discrete = TRUE) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  ggtitle("Relation of Multilocus Genotypes and MCGs")

@@

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% mcgs$MCG[1:5])
top5g <- make_mcgmlg_graph(top5) %>% add_communities(cluster_walktrap(g))
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
set.seed(2017-05-04)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "nicely")
top5lay$community <- inner_join(data_frame(vertex = top5lay$name), the_communities)$comm
t5g <- mcg_mlg_graph %+% top5lay + ggtitle("Top 5 Mycelial Compatibility Groups and associated MLGs")
t5g
ggsave(t5g, file = file.path("results", "figures", "publication", "FigureS2B.svg"), width = 88, height = 88, scale = 3, units = "mm")
```
